### 2023-11-20 chapters/paper_retrospective.tex
Add source reference at the top of every paper chapter
Fix references

\chapter[a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{chp:paper-retrospective}
\ifthenelse{\equal{\skippapers}{true}}{}{

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure1.pdf}
    \caption[ROC- and PPV-sensitivity curves for stroke recognition model.]{Receiver operator characteristic (ROC) curve and PPV-sensitivity curve. Left, the ROC curve and, right, PPV-sensitivity curve (precision-recall curve). Models 1-5 are the individual models that make up the ensemble model.}
    \label{fig_retrospective:figure1-roc-curve}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{paper_retrospective/figure2.pdf}
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \label{fig_retrospective:figure2-prediction-confusion-matrices}
\end{figure}

@@

As the threshold differed for each model in the ensemble, computing the ensemble output score as the average output score of the individual models would not be meaningful. Instead, we first subtracted the threshold from the output score in the logit space (before sigmoid nonlinearity) for each model to obtain the same threshold (0.5). Subsequently, we defined the ensemble output score as the average of the centred output scores. The exact equations are provided in \cref{app:supplementary-retrospective} in \cref{eq_retrospective:output_score, eq_retrospective:ensemble_prediction}.

>>>>

\chapter[a retrospective study on machine learning-assisted stroke recognition for medical helpline calls]{A Retrospective Study on Machine Learning-Assisted Stroke Recognition for Medical Helpline Calls}
\label{chp:paper-retrospective}

\textit{This chapter is a piece of original research published as part of the project:} \newline
\begin{center}
    \begin{enumerate}[leftmargin=8mm,rightmargin=8mm,topsep=0mm,label={[\Alph*]}]
        \setcounter{enumi}{5}
        \item \fullcite{wenstrup_retrospective_2023} \shared
    \end{enumerate}
\end{center}

\ifthenelse{\equal{\skippapers}{true}}{}{

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.95\textwidth]{paper_retrospective/figure1.pdf}
    \caption[ROC- and PPV-sensitivity curves for stroke recognition model.]{Receiver operator characteristic (ROC) curve and PPV-sensitivity curve. Left, the ROC curve and, right, PPV-sensitivity curve (precision-recall curve). Models 1-5 are the individual models that make up the ensemble model.}
    \label{fig_retrospective:figure1-roc-curve}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.98\textwidth]{paper_retrospective/figure2.pdf}
    \caption[Prediction confusion matrices for stroke recognition.]{Prediction confusion matrices. Confusion matrices of predictions for call takers and the model on the test set. Numbers for the model are given as the rounded mean over eleven runs.}
    \label{fig_retrospective:figure2-prediction-confusion-matrices}
\end{figure}

@@

As the threshold differed for each model in the ensemble, computing the ensemble output score as the average output score of the individual models would not be meaningful. Instead, we first subtracted the threshold from the output score in the logit space (before sigmoid nonlinearity) for each model to obtain the same threshold (0.5). Subsequently, we defined the ensemble output score as the average of the centred output scores. The exact equations are provided in \cref{eq_retrospective:output_score,eq_retrospective:ensemble_prediction}.
